---
title: "Lab 01: linear algebra + computing review"
subtitle: "Ikea furniture"
author: Josh, Lida, Ava
date: "August 31, 2026"
format: pdf
editor: visual
---

## Setup

Load packages and data:

```{r}
#| label: load-pkg-data
#| message: false
#| warning: false


library(tidyverse)
library(tidymodels)
ikea <- read_csv("data/ikea.csv")
```

\pagebreak

## Linear algebra review

\[Delete the placeholders for Exercises 1 - 6 if you are submitting handwritten responses for these exercises\]

### Exercise 1

Attached at end of pdf

\pagebreak

### Exercise 2

Attached at end of pdf

\pagebreak

### Exercise 3

Attached at end of pdf

\pagebreak

### Exercise 4

Attached at end of pdf

\pagebreak

### Exercise 5

Attached at end of pdf

\pagebreak

### Exercise 6

Attached at end of pdf

\pagebreak

## Computing review

### Exercise 7

```{r}
#| label: ex-07
library(tidyverse) 
library(knitr)
ikea <- read_csv("data/ikea.csv")

```

```{R}
ggplot(data = ikea, aes(x = price_usd)) +
  geom_histogram() +
    labs(x = "Price in Dollars",
       y = "Number of Products", 
       title = "Distribution of Price (in Dollars) of Ikea Furniture 
       in April 2020")
```

\pagebreak

### Exercise 8

The median is more representative of the center than the mean as the distribution is right skewed with a few outliers with really high cost. This means that the mean would be "stretched" higher due to those really high cost items, when in reality there are only a few of them. For median, those outliers have significantly less impact, therefore the median is a better representative of the center of the distribution.

\pagebreak

### Exercise 9

```{R}
ikea_sub <- ikea |>
  filter(category %in% c( "Sofas & armchairs",
                       "Bookcases & shelving units"))

ikea_sub <- ikea_sub |>
  drop_na(width, price_usd)
```

There are 765 observations with 13 variables.
The advantage of deleting all observations with one or more missing variables is 
that we don't have to deal with NA values during computing of data. A disadvantage
would be that we have a smaller sample size
as we are completely removing the row, which could lead to things such as 
decreasing power. 

\pagebreak

### Exercise 10

```{R}
#| fig-cap: "There is a positive nonlinear relationship between Price and Width of Ikea Furniture"
ggplot(data = ikea_sub, aes(x = width, y = price_usd)) +
  geom_point() +
    labs(x = "Width of Furniture (in cm)",
       y = "Price in USD", 
       title = "Relationship Between Price (in USD) and Width (in cm) of \nIkea Furniture in April 2020")
```
```{R}
#| fig-cap: "As the width increases, the price of sofas and armchairs increase at a faster rate compared to bookcases and shelving units"
ggplot(data = ikea_sub, aes(x = width, y = price_usd, shape = category, color = category)) +
  geom_point() +
    labs(x = "Width of Furniture (in cm)",
       y = "Price in USD", 
       title = "Relationship Between Price (in USD) and Width (in cm) 
       of \nIkea Furniture in April 2020",
       color = "Furniture Category", 
       shape = "Furniture Category")
```
...
