---
title: "Lab 01: linear algebra + computing review"
subtitle: "Ikea furniture"
author: Josh, Lida, Ava
date: "August 31, 2026"
format: pdf
editor: visual
---

## Setup

Load packages and data:

```{r}
#| label: load-pkg-data
#| message: false
#| warning: false


library(tidyverse)
library(tidymodels)
ikea <- read_csv("data/ikea.csv")
```


\pagebreak

## Linear algebra review

\[Delete the placeholders for Exercises 1 - 6 if you are submitting handwritten responses for these exercises\]

### Exercise 1

Attached at end of pdf

\pagebreak

### Exercise 2

Attached at end of pdf

\pagebreak

### Exercise 3

Attached at end of pdf

\pagebreak

### Exercise 4

Attached at end of pdf

\pagebreak

### Exercise 5

Attached at end of pdf

\pagebreak

### Exercise 6

Attached at end of pdf

\pagebreak

## Computing review

### Exercise 7

```{r}
#| label: ex-07
library(tidyverse) 
library(knitr)
ikea <- read_csv("data/ikea.csv")

```

```{R}
ggplot(data = ikea, aes(x = price_usd)) +
  geom_histogram() +
    labs(x = "Price in Dollars",
       y = "Number of Products", 
       title = "Distribution of Price (in Dollars) of Ikea Furniture 
       in April 2020")
```

\pagebreak

### Exercise 8

The median is more representative of the center than the mean as the distribution
is right skewed with a few outliers with really high cost. This means that the mean would be "stretched" higher due to those really high cost items, when in 
reality there are only a few of them. For median, those outliers have significantly less impact, therefore the median is a better representative of the
center of the distribution. 

\pagebreak

### Exercise 9

```{R}
ikea_sub <- ikea |>
  filter(category %in% c( "Sofas & armchairs",
                       "Bookcases & shelving units"))

ikea_sub <- ikea_sub |>
  drop_na(width, price_usd)
```
There are 765 observations with 13 variables.

\pagebreak

### Exercise 10

...
